Wigglyhedra

### 2025-01-04 draft/wigglyhedra.tex
missing files

We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$.

>>>>

We now show that the $\b{g}$-vectors of \cref{def:gvectors} support a polyhedral fan realization of the wiggly complex~$\wigglyComplex_n$ illustrated in \cref{fig:wigglyFan}.
\afterpage{
\begin{figure}
\centerline{\includegraphics[scale=.75]{wigglyFan}}
\caption{The wiggly fan~$\wigglyFan_2$, intersected with the unit sphere and projected stereographically to the plane.}
\label{fig:wigglyFan}
\end{figure}
}
